Reanalysis Step 7: Sample Comparison Table

### 2025-09-04 reanalysis-7-missingness_patterns.qmd
data comparison

# 2. Load new data with cohort assignments (from reanalysis-1)
cohort_file <- file.path(reanalysis_data_dir, "df_with_cohort.rds")
if (!file.exists(cohort_file)) {
  stop("Cohort data not found. Run reanalysis-1-data_preparation.qmd first.")
}
cohort_data <- readRDS(cohort_file)

# Split into submitted and excluded
submitted_data <- cohort_data[cohort_data$cohort_id == "submitted", ]
excluded_data <- cohort_data[cohort_data$cohort_id == "excluded", ]

>>>>

# 2. Load new complete cases data (from reanalysis-1)
complete_file <- file.path(reanalysis_data_dir, "df_complete_original.rds")
if (!file.exists(complete_file)) {
  stop("Complete cases data not found. Run reanalysis-1-data_preparation.qmd first.")
}
complete_data <- readRDS(complete_file)

# Split into submitted and excluded based on cohort_id
submitted_data <- complete_data[complete_data$cohort_id == "submitted", ]
excluded_data <- complete_data[complete_data$cohort_id == "excluded", ]
